Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-09-07 pnas/Towards.tex
Wrote an abstract

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here. \revised{Let's leave it open for now} }
\authordeclaration{The authors declare no conflicts of interest.}
%\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: tamir.bendory@princeton.edu}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
\keywords{Keyword 1 $|$ Keyword 2 $|$ Keyword 3 $|$ ...}

@@

\begin{abstract}

Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

>>>>

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here. \revised{Let's leave it open for now} }
\authordeclaration{The authors declare no conflicts of interest.}
%\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: tamir.bendory@princeton.edu \TODO{Should this be Amit's address?}}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
\keywords{Cryo-EM $|$ autocorrelation analysis $|$ detection limit}

@@

\begin{abstract}
{C}ryo--electron microscopy (cryo--EM) is used in structural biology to determine the 3-D structure of molecules. In a cryo-EM experiment, the microscope produces images called micrographs. Projections of the molecule of interest are embedded in the micrographs at unknown locations, and under unknown viewing directions. Standard imaging techniques first locate these projections (detection), then reconstruct the 3-D structure from them. Unfortunately, high noise levels hinder detection. When reliable detection is rendered impossible, the standard techniques fail. This is a problem especially for small molecules, which can be particularly hard to detect. In this paper, we propose a radically different approach: we contend that the structure could, in principle, be reconstructed directly from the micrographs, without intermediate detection and independently of the noise level (provided sufficiently many micrographs are acquired). As a result, even small molecules should be within reach for cryo-EM. To support this claim, we setup a simplified mathematical model and demonstrate how our autocorrelation-based techniques allow to go directly from the micrographs to the sought signals. This involves only one pass over the micrographs, which is desirable for large experiments. Furthermore, concerns regarding experimental bias are reduced as we do not require particle picking via pattern matching. We detail elementary theory for a 1-D version of the simplified model and show how to extend it to 2-D and to single particle reconstruction from synthetic cryo-EM data. We show numerical results, then discuss challenges that lay ahead to turn this proof-of-concept into a competitive alternative to state-of-the-art algorithms.
%Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}
